%-------------------------
% Resume in Latex
% Author : Radhakrishnan Ravi Vignesh
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resitem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-8 pt}}
  }
}
\newcommand{\ritem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}


\newcommand{\resumeSubHeadingListStart}{\begin{description}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{description}\vspace{-6pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Radhakrishnan Ravi Vignesh}\\
  \href{https://www.github.com/vigneshr97}{Github: https://www.github.com/vigneshr97} & Mobile: +1-979-676-6684 \\
  \href{https://www.linkedin.com/in/vigneshr97}{Linkedin: https://www.linkedin.com/in/vigneshr97} & Email: \href{mailto:vigneshr97@gmail.com}{vigneshr97@gmail.com}
\end{tabular*}\vspace{-8pt}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {Master of Science in Civil Engineering;  Specialization: Transportation Engineering}{Aug. 2018 -- Present}
    \resumeSubheading
      {Indian Institute of Technology Madras}{Chennai, India}
      {B.Tech in Civil Engineering; Minor: Industrial Engineering; CGPA: 8.01/10.00}{Aug. 2014 -- July. 2018}
  \resumeSubHeadingListEnd

%-----------INTERESTS------------------
\section{Interests}
   \resumeSubHeadingListStart
    \ritem
      {Network Optimization, Computer Vision, Deep Learning}
  \resumeSubHeadingListEnd
  
%-----------SKILLS------------------
\section{Relevant Technical Skills}
   \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}
      {C, C++, Python, R}
    \resumeSubItem{Libraries}
      {Numpy, OpenCV, Scikit Learn, Pandas, Tensorflow, Keras, Eigen(C++)}
    \resumeSubItem{Software Skills}
      {AutoCAD, Revit, MATLAB, Civil 3D, \LaTeX , git}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor’s Thesis: Optimization of Network Algorithms}{IIT Madras}
      {Advisor: Dr. Karthik K Srinivasan}{Aug 2017 - June 2018}
      \justifying\resumeItemListStart
        \ritem{Optimized the label setting algorithm given by D.Shier for finding the best K elementary paths in a directed graph and bench marked against other best known algorithms such as that of \href{http://www.dis.uniroma1.it/challenge9/papers/pascoal.pdf}{Marta M.B Pascoal} and Hoffman \& Pavley.}
        \ritem{Experiments were performed on randomized grid networks and real world networks and compared with other existing algorithms. The algorithm performed significantly better than other algorithms asymptotically.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Tamil Nadu Health Systems Project)}{Government of Tamil Nadu, India}
      {Software Developer Intern}{May 2017 - July 2017}
      \justifying\resumeItemListStart
        \ritem
          {Developed a heuristic algorithm with an accuracy of over 90\% to find the victim pickup locations of emergency vehicles and hence automating the data entry of victim pickup time and hospital reach time of the vehicles.}
        \ritem
          {The zonal distribution of calls was used to allocation ambulances with an optimal scene arrival time.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Udacity Projects}
  \resumeItemListStart
    \justifying\resumeSubItem{Behavioral Cloning}
      {Trained a simulator to drive a car around a track smoothly. An \textbf{image regression} model was developed after performing various modifications on NVIDIA's deep neural network architecture using \textbf{Transfer learning} technique. \textbf{Keras} library was used in the implementation.}
    \justifying\resumeSubItem{Traffic Sign Classifier}
      {Developed a traffic sign classifier model with a deep neural network architecture similar to \textbf{LeNet} using Tensorflow library and obtained \textbf{94\%} test accuracy using German Traffic sign data set. Various \textbf{data augmentation} techniques were employed to arrive at a higher accuracy.}
    \justifying\resumeSubItem{Lane Detection}
      {The lane region and the radii of curvature of the lane boundaries were detected in a video recorded from a car. The video involved various brightness and shadow levels along with different textures on the road.}
    \justifying\resumeSubItem{Extended Kalman Filters}
      {The measurements from a noisy Laser and a noisy Radar were \textbf{fused} using Kalman Filter and Extended Kalman Filter Equations and the position and velocity of objects were detected.}
  \resumeItemListEnd

%-----------COURSEWORK----------------
\section{Coursework}
  \resumeSubHeadingListStart
    \justifying\resumeSubItem{Texas A\&M}
    {Urban Transportation Planning, Traffic Engineering: Characteristics, Street and Highway Design}
    \justifying\resumeSubItem
      {IIT Madras}{Transportation Network Analysis, Analytical Techniques in Transportation Engineering, Urban Transportation Planning, Fundamentals of Operations Research, Industrial Engineering, Computer Simulation, Computer Applications in Transportation Engineering, Decision Modelling, Probability and Statistics, Differential Equations}
    \justifying\resumeSubItem
      {Udacity}{Computer Vision, Deep Learning, Sensor Fusion}
  \resumeSubHeadingListEnd

%-----------TEST SCORES-----------------
\section{Test Scores}
  \resumeSubHeadingListStart
    \resumeSubItem{GRE}
      {Q: 170/170; V: 149/170; AW: 3.5/6}
    \resumeSubItem{TOEFL iBT}
      {R: 26/30; L: 26/30; S: 22/30; W: 25/30}
  \resumeSubHeadingListEnd

%-----------EXTRA CURRICULAR ACTIVITIES-----------------
\section{Extra Curricular Activities}
  \resumeSubHeadingListStart
    \ritem{\textbf{Captain} of IIT Madras Squash Team during 2017-18 leading to a silver medal finish in the Inter Collegiate Sports Fest}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
